Estimating Output Loss due to being Unrecognized as States

### 2019-03-11 paper/paper.tex
Place figure captions above the figures #37 #44
Use en dash where appropriate #56

The empirical challenge for such endeavor is the lack of data. International organizations such as the World Bank do not provide any data for unrecognized states. 
The limited state capacity of these territories implies that there is no official statistics. 
Any surveys conducted in their parent countries exclude these territories from the sampling procedure.%
\footnote{%
	As an example, the Demographic and Health Survey conducted in Moldova in 2005 excludes the entire Transnistria from its sample (National Scientific and Applied Center for Preventive Medicine 2006: xxvi).
} 
To overcome this data limitation, the present study uses the satellite images of nighttime light for the period 1993-2013 to recover the unobserved annual economic growth rates of the four unrecognized states in the former Soviet Union.

@@

In 1923, the Soviet Union's authority drew the border of Nagorno-Karabakh Autonomous Oblast from scratch, based on their understanding of where Armenians resided within Azerbaijan.%
\footnote{
	An autonomous oblast is a district with some degree of autonomy from the government of a constituent republic of the Soviet Union. 
} 
The Soviet leaders made Nagorno-Karabakh part of Azerbaijan, rather than of Armenia, for two reasons, according to de Waal (2013: 144-145). First, Moscow needed to appease Azeri politicians to control their oil fields in the Caspian Sea. Second, Armenians in Nagorno-Karabakh economically relied on the eastern part of Azerbaijan, and the communist ideal dictated that economic consideration should override ethnic integration.

During the Soviet days, the Azerbaijani authority encouraged the migration of Azeris into Nagorno-Karabakh. Population of Azerbaijanis in Nagorno-Karabakh jumped up from 13,000 in 1926 to 37,000 in 1979 while the corresponding figures for Armenians are 117,000 and 123,000, respectively (de Waal 2013: 153-154). The Azeri authority also ignored the Armenian culture in Nagorno-Karabakh: there was no Armenian-language television channel; the history of Armenia not taught in Armenian-language schools; medieval Armenian churches closed and crumbling (de Waal 2013: 154).

@@

Information is scant on economic conditions in Nagorno-Karabakh since the 1994 ceasefire. 
International Crisis Group (2005: 14-15) provides a rare account of Karabakh's economy as follows. 
\begin{itemize}
\item Entrepreneurs have been engaged in profitable scrap metal businesses by dismantling infrastructure, housing and other pre-war structures for the resale of metal, bricks and building materials in the occupied territory of Azerbaijan.
\item Privatization of land and state enterprises has largely been completed. All residents outside the capital city of Stepanakert received 0.6 hectares of arable land. Private companies account for 80\% of the output. 
\item Under-employment is widespread among rural residents although officials claim that the unemployment rate was 5.6\% in 2003. In 2005, the government started providing the unemployed with 60\% of the minimum wage.
\item The government encourages child birth through various benefits for children: large families receive free electricity and books; couples with three children or more receive cash grants; and those with six children or more are given new homes.
\item Income inequality is growing. In a survey of 1,000 by Stepanakert Press Club in October 2003, 40.5\% of the respondents answered that they lived better than five years ago while 57.6\% said their life got worse or didn't change.
\end{itemize}

On the other hand, Azerbaijan proper has experienced economic growth thanks to oil exports. 
In 2006, the oil pipeline was opened from Baku, the capital city, to Turkey via Georgia, contributing to the world's fastest economic growth from 2005 to 2008 (de Waal 2013: 291-292). 
World Bank (2006: Table 1) reports that the percentage of people living in poverty fell from 44.6\% in 2002 to 24.0\% in 2005.
This rapid decline is not concentrated in Baku and other urban areas but also seen in rural areas.

@@

% Comparison to WDI
An alternative data source for real GDP is World Development Indicators (World Bank 2018). 
We prefer the Penn World Table, however, because since version 8 it makes real GDP cross-sectionally comparable in multiple years. 
The cross-sectional comparability in the World Development Indicators is only ensured for the latest international price survey year (2010 for the latest version); the farther away from this reference year, the less comparable its data on real GDP across countries (see Pinkovskiy and Sala-i-Martin 2016, sections 2.1-2.2, for detail).
As we exploit the variation in nighttime light not only within each country but also within each year, cross-sectional comparability is important.

@@

The Soviet-era boundaries accurately delineate the territories controlled by Abkhazia and South Ossetia after 2008 only, however. As a result of the wars of secession in 1991-1992, the north-east of Abkhazia (Upper Kodor Gorge) was under the control of Georgia proper (Tsutsiev 2014: Map 43). 
For South Ossetia, villages with Georgian residents were under the control of Georgia proper (Tsutsiev 2014: Map 42). 
In 2008, the defeat of Georgia against Russia resulted in the expulsion of the Georgian forces entirely from the Soviet-era territory of Abkhazia (Schwirtz 2008) and South Ossetia (O'Loughlin et al.\ 2014: 428).

Since the data is unavailable for the pre-2008 boundaries of effectively controlled areas by Abkhazia and South Ossetia, this study uses the Soviet-era boundaries throughout the sample period of 1992-2013.

@@

\section{Results}
\subsection{Fixed Effects Estimation Results}
The results from estimating equation (\ref{gdp}) are reported in Table \ref{estimates}. 
The elasticity of real GDP with respect to nighttime light intensity is 0.35 (significant at the 1\% level).
This estimate is largely comparable to what the literature has found.%
\footnote{
	Henderson et al.\ (2012: Table 2) report the elasticity of 0.28 for the sample period of 1992-2008. Hodler and Raschky (2014: Appendix B) find the elasticity of 0.39 for subnational regions across the world for 1992-2009. Storeygard (2016: Table 1) obtains the elasticity of 0.25 for Chinese cities and prefectures for 1990-2005. 
}   
Year fixed effect estimates are also reported in Table \ref{estimates} as these values will be used to predict annual real GDP growth for unrecognized states. 
Note that the adjusted R-squared is 0.99. 
The model represented in equation (\ref{gdp}) explains almost all the variations in real GDP across countries and over time.

@@

\subsection{Validation}
We first validate our methodology by comparing the predicted growth with the actual growth of real GDP from the Penn World Table for the three parent countries. 
% Azerbaijan
Figure \ref{aze} shows the results for Azerbaijan.
For years 1993-2004 and 2012-2013, the predicted growth rates do not align well with the actual growth rates, even showing a wrong sign in some years. 
From 2005 to 2011, however, the predicted growth rates capture the trend in the actual growth rates. 
The predicted growth generally underestimates the actual growth, probably because nighttime light does not capture the GDP growth due to world oil price hikes.%
\footnote{
	As discussed in Section \ref{background}, Azerbaijan became an oil exporter with major oil pipelines opened in 2006. 
	World oil prices surged during the period of 2005-2008. 
}
% Georgia
Figure \ref{geo} compares the actual growth rates with the predicted ones for Georgia. 
Similarly to Azerbaijan, years 1993-2003 see discrepancies between the predicted and actual growth rates, with opposite signs in some years. 
For years 2004-2013, however, the predicted growth roughly picks up the trend in the actual growth, with the magnitude also comparable.
% Moldova
Figure \ref{mda} shows the results for Moldova.
For years 1993-2003 and 2011-2013, the predicted growth deviates from the actual growth, with a wrong sign in some years.
Years 2004-2010 see the predicted growth approximate the actual growth relatively well.
% Summary
Overall, the predicted growth around years 2004-2010 is trustworthy. 
Outside this period, either our prediction methodology fails or the official GDP statistics from these countries is prone to errors.%
\footnote{
	The discrepancies in the 1990s may be due to the incapability of statistical offices in these countries to provide accurate GDP figures in the aftermath of the collapse of the socialist economic system. 
	This explanation, however, does not account for why there are also discrepancies in the 2010s.
}

@@

\paragraph{Nagorno-Karabakh}
Figure \ref{nkr} shows the predicted annual real GDP growth rates for Nagorno-Karabakh in comparison to the predicted growth for its parent country, Azerbaijan. 
For years 1993-1995, Karabakh's economy is estimated to have shrunk by over 10\% annually, reflecting the damage from the war of secession from Azerbaijan. 
From 1996 to 2004, the estimated economic growth was very volatile.
For the period 2005-2011, where Azerbaijan's predicted growth rates trace the trend in the actual growth, Nagorno-Karabakh's economic growth exceeds 10\% (except for 2009 and 2011). 
These growth rates exceed the predicted growth rates in Azerbaijan proper.
It may just reflect the higher marginal product of capital per worker in Nagorno-Karabakh as the territory is poorer than the rest of Azerbaijan. 
However, it may also suggest that the impact of being unrecognized as a sovereign state is minimal in terms of economic recovery from civil wars in the case of Nagorno-Karabakh.

\paragraph{Abkhazia}
Figure \ref{abk} shows the predicted annual real GDP growth for Abkhazia in comparison to the predicted growth in Georgia proper. 
For years 1993-2003, the estimated economic growth rates are very volatile in Abkhazia though the ones in Georgia are equally volatile as well.
For the period 2004-2013, when Georgia's predicted growth corresponds well with its actual growth, Abkhazia's growth rates are positive and largely comparable to Georgia's growth.   
Overall, the impact of being unrecognized as a sovereign state appears to be minimal in the case of Abkhazia as long as Georgia proper is a valid counterfactual.

\paragraph{South Ossetia}
Figure \ref{sos} compares the predicted growth rates for South Ossetia with the ones for Georgia proper.
For the period 2004-2013, when Georgia's predicted and actual growth rates co-move, South Ossetia's predicted growth is comparable to Georgia's.
From 2010, South Ossetia outperforms Georgia in predicted growth, probably reflecting the consequences of South Ossetian War in 2008: Russia actively helps South Ossetia financially while Georgia loses its trade with Russia.

\paragraph{Transnistria}
Finally, Figure \ref{tra} reports the predicted economic growth rates for Transnistria in comparison to those for Moldova proper. 
Transnistria's predicted economic growth is volatile during the entire sample period, including years 2004-2010, when Moldova's predicted and actual real GDP growth rates correspond well to each other. 
Its magnitude is overall smaller than the other three unrecognized states.
The same remarks apply to its parent country, Moldova, suggesting that the impact of being unrecognized as a sovereign state is minimal in the case of Transnistria.

@@

\bibitem{} Bauer, Michal, Christopher Blattman, Julie Chytilova, Joseph Henrich, Edward Miguel, and Tamar Mitts. 2016. ``Can War Foster Cooperation?'' \textit{Journal of Economic Perspectives}, 30(3): 249-274.

@@

\bibitem{} Bickenbach, Frank, Eckhardt Bode, Peter Nunnenkamp, and Mareike Soder. 2016. ``Night lights and regional GDP.'' \textit{Review of World Economics}, 152 (2), 425-447.
\bibitem{} Blattman, Christopher, and Edward Miguel. 2010. ``Civil War.'' \textit{Journal of Economic Literature}, 48(1): 3-57.                                                                                   
\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238-249.
\bibitem{} Casey, K., R. Glennerster, and E. Miguel. 2012. ``Reshaping Institutions: Evidence on Aid Impacts Using a Preanalysis Plan.'' \textit{The Quarterly Journal of Economics}, 127(4): 1755-1812.

@@

\bibitem{} Feenstra, Robert C., Robert Inklaar, and Marcel P. Timmer. 2015. ``The Next Generation of the Penn World Table.'' \textit{American Economic Review}, 105(10): 3150-3182.

@@

\bibitem{} Henderson, J. Vernon, Adam Storeygard, and David N. Weil. 2012. ``Measuring Economic Growth from Outer Space.'' \textit{American Economic Review}, 102(2): 994-1028.
\bibitem{} Hodler, Roland, and Paul A. Raschky. 2014. ``Regional Favoritism.'' \textit{Quarterly Journal of Economics}, 129(2): 995-1033.

@@

@@

\bibitem{} O'Loughlin, John, Vladimir Kolossov, and Gerard Toal. 2014. ``Inside the Post-Soviet de Facto States: A Comparison of Attitudes in Abkhazia, Nagorny Karabakh, South Ossetia, and Transnistria.'' \textit{Eurasian Geography and Economics}, 55(5): 423-456.

@@

\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{The Review of Economic Studies}, 83(3): 1263-1295.

@@

\bibitem{} Witmer, Frank D.W., and John O?Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478-500.
\bibitem{} World Bank. 2006. ``Country Partnership Strategy FY07-10 for Republic of Azerbaijan.'' South Caucasus Country Management Unit, the World Bank.

@@

\begin{figure}[ptb]
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_AZE.png}
\caption{Actual and Predicted Annual Real GDP Growth in Azerbaijan}
\label{aze}%
{\scriptsize \textbf{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Azerbaijan proper, excluding the territory occupied by Nagorno-Karabakh's authority. 
}
\end{figure}

\begin{figure}[ptb]
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_GEO.png}
\caption{Actual and Predicted Annual Real GDP Growth in Georgia}
\label{geo}%
{\scriptsize \textbf{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Georgia proper, excluding the Soviet-era territories of Abkhazia and South Ossetia. 
}
\end{figure}

\begin{figure}[ptb]
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_MDA.png}
\caption{Actual and Predicted Annual Real GDP Growth in Moldova}
\label{mda}%
{\scriptsize \textbf{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Moldova proper, excluding the Soviet-era territory of Transnistria. 
	The actual growth in 1993 is very close to zero, rather than being missing in the data source.
}
\end{figure}

\begin{figure}[ptb]
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_NKR.png}
\caption{Predicted Annual Real GDP Growth in Nagorno-Karabakh and Azerbaijan}
\label{nkr}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for Nagorno-Karabakh is due to the author's calculation (see the text for detail).
	The corresponding data for Azerbaijan is the same as in Figure \ref{aze}.
}
\end{figure}

\begin{figure}[ptb]
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_ABK.png}
\caption{Predicted Annual Real GDP Growth in Abkhazia and Georgia}
\label{abk}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for Abkhazia is due to the author's calculation (see the text for detail).
	The corresponding data for Georgia is the same as in Figure \ref{geo}.
}
\end{figure}

\begin{figure}[ptb]
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_SOS.png}
\caption{Predicted Annual Real GDP Growth in South Ossetia and Georgia}
\label{sos}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for South Ossetia is due to the author's calculation (see the text for detail).
	The corresponding data for Georgia is the same as in Figure \ref{geo}.
}
\end{figure}

\begin{figure}[ptb]
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_TRA.png}
\caption{Predicted Annual Real GDP Growth in Transnistria and Moldova}
\label{tra}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for Transnistria is due to the author's calculation (see the text for detail).
	The corresponding data for Moldova is the same as in Figure \ref{mda}.
}
\end{figure}

>>>>

The empirical challenge for such endeavor is the lack of data. International organizations such as the World Bank do not provide any data for unrecognized states. 
The limited state capacity of these territories implies that there is no official statistics. 
Any surveys conducted in their parent countries exclude these territories from the sampling procedure.%
\footnote{%
	As an example, the Demographic and Health Survey conducted in Moldova in 2005 excludes the entire Transnistria from its sample (National Scientific and Applied Center for Preventive Medicine 2006: xxvi).
} 
To overcome this data limitation, the present study uses the satellite images of nighttime light for the period 1993--2013 to recover the unobserved annual economic growth rates of the four unrecognized states in the former Soviet Union.

@@

In 1923, the Soviet Union's authority drew the border of Nagorno-Karabakh Autonomous Oblast from scratch, based on their understanding of where Armenians resided within Azerbaijan.%
\footnote{
	An autonomous oblast is a district with some degree of autonomy from the government of a constituent republic of the Soviet Union. 
} 
The Soviet leaders made Nagorno-Karabakh part of Azerbaijan, rather than of Armenia, for two reasons, according to de Waal (2013: 144--145). First, Moscow needed to appease Azeri politicians to control their oil fields in the Caspian Sea. Second, Armenians in Nagorno-Karabakh economically relied on the eastern part of Azerbaijan, and the communist ideal dictated that economic consideration should override ethnic integration.

During the Soviet days, the Azerbaijani authority encouraged the migration of Azeris into Nagorno-Karabakh. Population of Azerbaijanis in Nagorno-Karabakh jumped up from 13,000 in 1926 to 37,000 in 1979 while the corresponding figures for Armenians are 117,000 and 123,000, respectively (de Waal 2013: 153--154). The Azeri authority also ignored the Armenian culture in Nagorno-Karabakh: there was no Armenian-language television channel; the history of Armenia not taught in Armenian-language schools; medieval Armenian churches closed and crumbling (de Waal 2013: 154).

@@

Information is scant on economic conditions in Nagorno-Karabakh since the 1994 ceasefire. 
International Crisis Group (2005: 14--15) provides a rare account of Karabakh's economy as follows. 
\begin{itemize}
\item Entrepreneurs have been engaged in profitable scrap metal businesses by dismantling infrastructure, housing and other pre-war structures for the resale of metal, bricks and building materials in the occupied territory of Azerbaijan.
\item Privatization of land and state enterprises has largely been completed. All residents outside the capital city of Stepanakert received 0.6 hectares of arable land. Private companies account for 80\% of the output. 
\item Under-employment is widespread among rural residents although officials claim that the unemployment rate was 5.6\% in 2003. In 2005, the government started providing the unemployed with 60\% of the minimum wage.
\item The government encourages child birth through various benefits for children: large families receive free electricity and books; couples with three children or more receive cash grants; and those with six children or more are given new homes.
\item Income inequality is growing. In a survey of 1,000 by Stepanakert Press Club in October 2003, 40.5\% of the respondents answered that they lived better than five years ago while 57.6\% said their life got worse or didn't change.
\end{itemize}

On the other hand, Azerbaijan proper has experienced economic growth thanks to oil exports. 
In 2006, the oil pipeline was opened from Baku, the capital city, to Turkey via Georgia, contributing to the world's fastest economic growth from 2005 to 2008 (de Waal 2013: 291--292). 
World Bank (2006: Table 1) reports that the percentage of people living in poverty fell from 44.6\% in 2002 to 24.0\% in 2005.
This rapid decline is not concentrated in Baku and other urban areas but also seen in rural areas.

@@

% Comparison to WDI
An alternative data source for real GDP is World Development Indicators (World Bank 2018). 
We prefer the Penn World Table, however, because since version 8 it makes real GDP cross-sectionally comparable in multiple years. 
The cross-sectional comparability in the World Development Indicators is only ensured for the latest international price survey year (2010 for the latest version); the farther away from this reference year, the less comparable its data on real GDP across countries (see Pinkovskiy and Sala-i-Martin 2016, sections 2.1--2.2, for detail).
As we exploit the variation in nighttime light not only within each country but also within each year, cross-sectional comparability is important.

@@

The Soviet-era boundaries accurately delineate the territories controlled by Abkhazia and South Ossetia after 2008 only, however. As a result of the wars of secession in 1991--1992, the north-east of Abkhazia (Upper Kodor Gorge) was under the control of Georgia proper (Tsutsiev 2014: Map 43). 
For South Ossetia, villages with Georgian residents were under the control of Georgia proper (Tsutsiev 2014: Map 42). 
In 2008, the defeat of Georgia against Russia resulted in the expulsion of the Georgian forces entirely from the Soviet-era territory of Abkhazia (Schwirtz 2008) and South Ossetia (O'Loughlin et al.\ 2014: 428).

Since the data is unavailable for the pre-2008 boundaries of effectively controlled areas by Abkhazia and South Ossetia, this study uses the Soviet-era boundaries throughout the sample period of 1992--2013.

@@

\section{Results}
\subsection{Fixed Effects Estimation Results}
The results from estimating equation (\ref{gdp}) are reported in Table \ref{estimates}. 
The elasticity of real GDP with respect to nighttime light intensity is 0.35 (significant at the 1\% level).
This estimate is largely comparable to what the literature has found.%
\footnote{
	Henderson et al.\ (2012: Table 2) report the elasticity of 0.28 for the sample period of 1992--2008. Hodler and Raschky (2014: Appendix B) find the elasticity of 0.39 for subnational regions across the world for 1992--2009. Storeygard (2016: Table 1) obtains the elasticity of 0.25 for Chinese cities and prefectures for 1990--2005. 
}   
Year fixed effect estimates are also reported in Table \ref{estimates} as these values will be used to predict annual real GDP growth for unrecognized states. 
Note that the adjusted R-squared is 0.99. 
The model represented in equation (\ref{gdp}) explains almost all the variations in real GDP across countries and over time.

@@

\subsection{Validation}
We first validate our methodology by comparing the predicted growth with the actual growth of real GDP from the Penn World Table for the three parent countries. 
% Azerbaijan
Figure \ref{aze} shows the results for Azerbaijan.
For years 1993--2004 and 2012--2013, the predicted growth rates do not align well with the actual growth rates, even showing a wrong sign in some years. 
From 2005 to 2011, however, the predicted growth rates capture the trend in the actual growth rates. 
The predicted growth generally underestimates the actual growth, probably because nighttime light does not capture the GDP growth due to world oil price hikes.%
\footnote{
	As discussed in Section \ref{background}, Azerbaijan became an oil exporter with major oil pipelines opened in 2006. 
	World oil prices surged during the period of 2005--2008. 
}
% Georgia
Figure \ref{geo} compares the actual growth rates with the predicted ones for Georgia. 
Similarly to Azerbaijan, years 1993--2003 see discrepancies between the predicted and actual growth rates, with opposite signs in some years. 
For years 2004--2013, however, the predicted growth roughly picks up the trend in the actual growth, with the magnitude also comparable.
% Moldova
Figure \ref{mda} shows the results for Moldova.
For years 1993--2003 and 2011--2013, the predicted growth deviates from the actual growth, with a wrong sign in some years.
Years 2004--2010 see the predicted growth approximate the actual growth relatively well.
% Summary
Overall, the predicted growth around years 2004--2010 is trustworthy. 
Outside this period, either our prediction methodology fails or the official GDP statistics from these countries is prone to errors.%
\footnote{
	The discrepancies in the 1990s may be due to the incapability of statistical offices in these countries to provide accurate GDP figures in the aftermath of the collapse of the socialist economic system. 
	This explanation, however, does not account for why there are also discrepancies in the 2010s.
}

@@

\paragraph{Nagorno-Karabakh}
Figure \ref{nkr} shows the predicted annual real GDP growth rates for Nagorno-Karabakh in comparison to the predicted growth for its parent country, Azerbaijan. 
For years 1993--1995, Karabakh's economy is estimated to have shrunk by over 10\% annually, reflecting the damage from the war of secession from Azerbaijan. 
From 1996 to 2004, the estimated economic growth was very volatile.
For the period 2005--2011, where Azerbaijan's predicted growth rates trace the trend in the actual growth, Nagorno-Karabakh's economic growth exceeds 10\% (except for 2009 and 2011). 
These growth rates exceed the predicted growth rates in Azerbaijan proper.
It may just reflect the higher marginal product of capital per worker in Nagorno-Karabakh as the territory is poorer than the rest of Azerbaijan. 
However, it may also suggest that the impact of being unrecognized as a sovereign state is minimal in terms of economic recovery from civil wars in the case of Nagorno-Karabakh.

\paragraph{Abkhazia}
Figure \ref{abk} shows the predicted annual real GDP growth for Abkhazia in comparison to the predicted growth in Georgia proper. 
For years 1993--2003, the estimated economic growth rates are very volatile in Abkhazia though the ones in Georgia are equally volatile as well.
For the period 2004--2013, when Georgia's predicted growth corresponds well with its actual growth, Abkhazia's growth rates are positive and largely comparable to Georgia's growth.   
Overall, the impact of being unrecognized as a sovereign state appears to be minimal in the case of Abkhazia as long as Georgia proper is a valid counterfactual.

\paragraph{South Ossetia}
Figure \ref{sos} compares the predicted growth rates for South Ossetia with the ones for Georgia proper.
For the period 2004--2013, when Georgia's predicted and actual growth rates co-move, South Ossetia's predicted growth is comparable to Georgia's.
From 2010, South Ossetia outperforms Georgia in predicted growth, probably reflecting the consequences of South Ossetian War in 2008: Russia actively helps South Ossetia financially while Georgia loses its trade with Russia.

\paragraph{Transnistria}
Finally, Figure \ref{tra} reports the predicted economic growth rates for Transnistria in comparison to those for Moldova proper. 
Transnistria's predicted economic growth is volatile during the entire sample period, including years 2004--2010, when Moldova's predicted and actual real GDP growth rates correspond well to each other. 
Its magnitude is overall smaller than the other three unrecognized states.
The same remarks apply to its parent country, Moldova, suggesting that the impact of being unrecognized as a sovereign state is minimal in the case of Transnistria.

@@

\bibitem{} Bauer, Michal, Christopher Blattman, Julie Chytilova, Joseph Henrich, Edward Miguel, and Tamar Mitts. 2016. ``Can War Foster Cooperation?'' \textit{Journal of Economic Perspectives}, 30(3): 249--274.

@@

\bibitem{} Bickenbach, Frank, Eckhardt Bode, Peter Nunnenkamp, and Mareike Soder. 2016. ``Night lights and regional GDP.'' \textit{Review of World Economics}, 152 (2), 425--447.
\bibitem{} Blattman, Christopher, and Edward Miguel. 2010. ``Civil War.'' \textit{Journal of Economic Literature}, 48(1): 3--57.                                                                                   
\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238--249.
\bibitem{} Casey, K., R. Glennerster, and E. Miguel. 2012. ``Reshaping Institutions: Evidence on Aid Impacts Using a Preanalysis Plan.'' \textit{The Quarterly Journal of Economics}, 127(4): 1755--1812.

@@

\bibitem{} Feenstra, Robert C., Robert Inklaar, and Marcel P. Timmer. 2015. ``The Next Generation of the Penn World Table.'' \textit{American Economic Review}, 105(10): 3150--3182.

@@

\bibitem{} Henderson, J. Vernon, Adam Storeygard, and David N. Weil. 2012. ``Measuring Economic Growth from Outer Space.'' \textit{American Economic Review}, 102(2): 994--1028.
\bibitem{} Hodler, Roland, and Paul A. Raschky. 2014. ``Regional Favoritism.'' \textit{Quarterly Journal of Economics}, 129(2): 995--1033.

@@

\bibitem{} Lee, Yong Suk. 2018. ``International Isolation and Regional Inequality: Evidence from Sanctions on North Korea.'' \textit{Journal of Urban Economics}, 103: 34--51.

@@

\bibitem{} O'Loughlin, John, Vladimir Kolossov, and Gerard Toal. 2014. ``Inside the Post-Soviet de Facto States: A Comparison of Attitudes in Abkhazia, Nagorny Karabakh, South Ossetia, and Transnistria.'' \textit{Eurasian Geography and Economics}, 55(5): 423--456.

@@

\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{The Review of Economic Studies}, 83(3): 1263--1295.

@@

\bibitem{} Witmer, Frank D.W., and John O?Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478--500.
\bibitem{} World Bank. 2006. ``Country Partnership Strategy FY07--10 for Republic of Azerbaijan.'' South Caucasus Country Management Unit, the World Bank.

@@

\begin{figure}[ptb]
\caption{Actual and Predicted Annual Real GDP Growth in Azerbaijan}
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_AZE.png}
\label{aze}%
{\scriptsize \textbf{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Azerbaijan proper, excluding the territory occupied by Nagorno-Karabakh's authority. 
}
\end{figure}

\begin{figure}[ptb]
\caption{Actual and Predicted Annual Real GDP Growth in Georgia}
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_GEO.png}
\label{geo}%
{\scriptsize \textbf{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Georgia proper, excluding the Soviet-era territories of Abkhazia and South Ossetia. 
}
\end{figure}

\begin{figure}[ptb]
\caption{Actual and Predicted Annual Real GDP Growth in Moldova}
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_MDA.png}
\label{mda}%
{\scriptsize \textbf{Notes}: 
	The data source for the actual annual real GDP growth is the Penn World Table (version 9.0). 
	The predicted annual real GDP growth is based on nighttime light intensity within Moldova proper, excluding the Soviet-era territory of Transnistria. 
	The actual growth in 1993 is very close to zero, rather than being missing in the data source.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in Nagorno-Karabakh and Azerbaijan}
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_NKR.png}
\label{nkr}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for Nagorno-Karabakh is due to the author's calculation (see the text for detail).
	The corresponding data for Azerbaijan is the same as in Figure \ref{aze}.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in Abkhazia and Georgia}
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_ABK.png}
\label{abk}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for Abkhazia is due to the author's calculation (see the text for detail).
	The corresponding data for Georgia is the same as in Figure \ref{geo}.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in South Ossetia and Georgia}
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_SOS.png}
\label{sos}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for South Ossetia is due to the author's calculation (see the text for detail).
	The corresponding data for Georgia is the same as in Figure \ref{geo}.
}
\end{figure}

\begin{figure}[ptb]
\caption{Predicted Annual Real GDP Growth in Transnistria and Moldova}
\includegraphics[width=\linewidth]{../a_output/plot_growth_hat_TRA.png}
\label{tra}%
{\scriptsize \textbf{Notes}: 
	The predicted annual real GDP growth for Transnistria is due to the author's calculation (see the text for detail).
	The corresponding data for Moldova is the same as in Figure \ref{mda}.
}
\end{figure}
